------------------------------------------------------------------------

------------------------------------------------------------------------

## [Overview]{style="color:royalblue"}

Here we provide the code used to create the results in our paper, and accompanying supplementary material. In order to run the code, please first download the data file "btbw_supercilium_data.csv" to your directory. See the "ReadMe.txt" file for descriptions of each variable.

```{r Downloads, warning=FALSE}

# Download Packages
#install.packages(c('dplyr', 'MASS'), dep=TRUE)

# Load Packages
library(dplyr) 
library(MASS)

# Load csv file
female_data <- read.csv("btbw_supercilium_data.csv")

female_data <- female_data %>%
  mutate(
    mass   = na_if(mass, 0),
    tarsus = na_if(tarsus, 0)
  )

# Remove 2 repeat individuals
repeat_ids <- female_data %>%
  filter(year %in% c(2021, 2022, 2023)) %>% count(combo) %>%
  filter(n > 1) %>% pull(combo)
female_data <- female_data %>% filter(!(combo %in% repeat_ids & year == 2022))

# Data transformations
female_data$f_prey <- sqrt(female_data$f_prey_biomass)
female_data$m_prey <- sqrt(female_data$m_prey_biomass)

# Within pair difference
female_data$delta_prey <- female_data$f_prey - female_data$m_prey

```

## [Plumage correlations]{style="color:royalblue"}

```{r Plumage, warning=FALSE}

sapply(female_data[, c("s_r_area", "s_r_bright")], function(x) {
  c(Min  = min(x, na.rm = TRUE), Max  = max(x, na.rm = TRUE),
    Mean = mean(x, na.rm = TRUE), SD   = sd(x, na.rm = TRUE),
    N    = sum(!is.na(x)) ) })

cor_size_lr <- cor.test(female_data$s_r_area, female_data$s_l_area, method = "pearson")
cor_size_lr

cor_bright_lr <- cor.test(female_data$s_r_bright, female_data$s_l_bright, method = "pearson")
cor_bright_lr

cor_size_bright <- cor.test(female_data$s_r_bright, female_data$s_r_area, method = "pearson")
cor_size_bright

cor_supercilium_undereye_size <- cor.test(female_data$s_r_area, female_data$u_r_area, method = "pearson")
cor_supercilium_undereye_size

cor_supercilium_undereye_bright <- cor.test(female_data$s_r_bright, female_data$u_r_bright, method = "pearson")
cor_supercilium_undereye_bright

# Differences between years
size.year.aov <- aov(s_r_area ~ factor(year), data = female_data)
summary(size.year.aov)
confint(size.year.aov)

bright.year.aov <- aov(s_r_bright ~ factor(year), data = female_data)
summary(bright.year.aov)
confint(bright.year.aov)

# Differences between elevation zones
size.elev.aov <- aov(s_r_area ~ factor(elevation), data = female_data)
summary(size.elev.aov)
confint(size.elev.aov)

bright.elev.aov <- aov(s_r_bright ~ factor(elevation), data = female_data)
summary(bright.elev.aov)
confint(bright.elev.aov)


```

## [Table 1]{style="color:royalblue"}

```{r Body measurments, warning=FALSE}
# Individual quality
body_measurment_comp_model <- lm(mass ~ tarsus + age + factor(year), data = female_data)
summary(body_measurment_comp_model)
confint(body_measurment_comp_model)

body_size_model <- lm(tarsus ~ s_r_area + s_r_bright + factor(year), data = female_data)
summary(body_size_model)
confint(body_size_model)

body_mass_model <- lm(mass ~ s_r_area + s_r_bright + factor(year), data = female_data)
summary(body_mass_model)
confint(body_mass_model)

female_data$factor_age <- factor(female_data$age)
age_model <- glm(factor_age ~ s_r_area + s_r_bright + factor(year), family = binomial, data = female_data)
summary(age_model)
confint(age_model)
```

## [Table 2]{style="color:royalblue"}

```{r Breeding outcomes, warning=FALSE}
# Reproductive correlates
reproductive_success_model <- glm.nb(n_fledge ~ s_r_area + s_r_bright + cid + factor(year),data = female_data)
summary(reproductive_success_model)
confint(reproductive_success_model)  

territory_quality_model <- lm(food_availability ~ s_r_area + s_r_bright + factor(year), data = female_data)

summary(territory_quality_model)
confint(territory_quality_model)

# Female provisioning
female_provisioning_model <- lm(f_prey ~ s_r_area + s_r_bright + factor(year), data = female_data)
summary(female_provisioning_model)
confint(female_provisioning_model)

# Male provisioning
male_provisioning_model <- lm(m_prey ~ s_r_area + s_r_bright + factor(year), data = female_data)
summary(male_provisioning_model)
confint(male_provisioning_model)


```

## [Bonferroni correction]{style="color:royalblue"}

```{r Breeding outcomes, warning=FALSE}

# Bonferroni correction
get_p <- function(model, term) {
  coefs <- summary(model)$coefficients
  coefs[term, "Pr(>|t|)"]
}

get_p_glm <- function(model, term) {
  coefs <- summary(model)$coefficients
  coefs[term, "Pr(>|z|)"]
}

p_values <- c(
  body_size_s_r_area       = get_p(body_size_model, "s_r_area"),
  body_size_s_r_bright     = get_p(body_size_model, "s_r_bright"),
  body_mass_s_r_area       = get_p(body_mass_model, "s_r_area"),
  body_mass_s_r_bright     = get_p(body_mass_model, "s_r_bright"),
  age_s_r_area             = get_p_glm(age_model, "s_r_area"),
  age_s_r_bright           = get_p_glm(age_model, "s_r_bright"),

  repro_success_s_r_area   = get_p_glm(reproductive_success_model, "s_r_area"),
  repro_success_s_r_bright = get_p_glm(reproductive_success_model, "s_r_bright"),
  territory_s_r_area       = get_p(territory_quality_model, "s_r_area"),
  territory_s_r_bright     = get_p(territory_quality_model, "s_r_bright"),
  female_prov_s_r_area     = get_p(female_provisioning_model, "s_r_area"),
  female_prov_s_r_bright   = get_p(female_provisioning_model, "s_r_bright"),
  male_prov_s_r_area       = get_p(male_provisioning_model, "s_r_area"),
  male_prov_s_r_bright     = get_p(male_provisioning_model, "s_r_bright")
)

p_adjusted <- p.adjust(p_values, method = "bonferroni")

bonferroni_results <- data.frame(
  test         = names(p_values),
  raw_p        = round(p_values, 4),
  bonferroni_p = round(p_adjusted, 4)
)

bonferroni_results


```

## [Figure S2]{style="color:royalblue"}

```{r Figure_S2, warning=FALSE}
# Size
hist(female_data$s_r_area, breaks = 15, main = "Histogram of supercilium size 2021-2023", 
     xlab = "Supercilium size (mm2)")
range(female_data$s_r_area)
mean(female_data$s_r_area) 
sd(female_data$s_r_area)
length(female_data$s_r_area)

# Brightness
hist(female_data$s_r_bright, breaks = 15,
     main = "Histogram of supercilium brightness 2021, 2023", 
     xlab = "Supercilium brightness (RGB)")
range(female_data$s_r_bright, na.rm=TRUE)
mean(female_data$s_r_bright, na.rm=TRUE) 
sd(female_data$s_r_bright, na.rm=TRUE)
length(female_data$s_r_bright[!is.na(female_data$s_r_bright)])


```
