------------------------------------------------------------------------

------------------------------------------------------------------------

## [Overview]{style="color:royalblue"}

Here we provide all of the code used to create the results in our paper "Little evidence of ornamental function for a female-specific plumage trait in the black-throated blue warbler", and accompanying supplementary material. In order to run the code, please first download the data file "btbw-supercilium_data.csv" to your working directory. See the "ReadMe.txt" file for descriptions of each variable.

```{r Downloads, warning=FALSE}

# Download Packages
install.packages(c('ggplot2', 'ggpubr', 'dplyr', 'tidyr', 'tidyverse', 'patchwork', 'lme4', 'lmerTest', 'plotrix', 'sjPlot', 'janitor'),dep=TRUE)

# Load Packages
library(ggplot2) 
library(ggpubr) 
library(dplyr) 
library(tidyr) 
library(tidyverse) 
library(patchwork) 
library(plotrix) 
library(sjPlot) 
library(janitor)

# Load csv file
female_data <- read.csv("btbw-supercilium_data.csv")
female_data %>% drop_na()

# Data transformations
#Square root transformation to normalize provisioning data
#Females
female_data$f_prov <- sqrt(female_data$f_provision_rate)
female_data$f_prey <- sqrt(female_data$f_prey_biomass)
female_data$f_attent <- sqrt(female_data$f_nest_attentiveness)
#Males
female_data$m_prey <- sqrt(female_data$m_prey_biomass)
female_data$m_attent <- sqrt(female_data$m_nest_attentiveness)
female_data$m_prov <- sqrt(female_data$m_provision_rate)

#Within pair difference
female_data$delta_prov <- female_data$f_prov - female_data$m_prov
female_data$delta_prey <- female_data$f_prey - female_data$m_prey
female_data$delta_attent <- female_data$f_attent - female_data$m_attent
```

## [Figures]{style="color:royalblue"}

**Figure 2 - Polygyny**

Mean difference in the conspicuousness of the female supercilium, including a) size, b) brightness, and c) contrast with lores between females paired to monogamous (left, “no”) or polygynous (right, “yes”) males in the black-throated blue warbler. Black points show mean values ± SE with error bars and gray points show supercilium conspicuousness values for each female.

```{r Figure_2, warning=FALSE}
#Size
#t = 1.7224, df = 27.657, p-value = 0.10
t.test(female_data$s_r_area ~ female_data$polygynous)

#Brightness
#t = 0.8091, df = 6.1553, p = 0.45
t.test(female_data$s_r_bright ~ female_data$polygynous)

#Contrast
#t = 2.3894, df = 8.6943, p = 0.042
t.test(female_data$r_cont ~ female_data$polygynous)


# Plot
p_1_polygyny <- ggerrorplot(data=subset(female_data, !is.na(polygynous)),
                  x = "polygynous", y = "s_r_area", 
                  desc_stat = "mean_sd", color = "black",
                  add = "jitter", add.params = list(color = "darkgray"), 
                  ylab = "Supercilium size (mm2)", xlab = "Mating strategy") + 
                  scale_x_discrete(labels=c("0"="Monogamous", "1"="Polygynous"))
p_2_polygyny <- ggerrorplot(data=subset(female_data, !is.na(polygynous)), 
                  x = "polygynous", y = "s_r_bright", 
                  desc_stat = "mean_sd", color = "black",
                  add = "jitter", add.params = list(color = "darkgray"), 
                  ylab = "Supercilium brightness (RGB)", xlab = "Mating strategy")+ 
                  scale_x_discrete(labels=c("0"="Monogamous", "1"="Polygynous"))
p_3_polygyny <- ggerrorplot(data=subset(female_data, !is.na(polygynous)), 
                  x = "polygynous", y = "r_cont", 
                  desc_stat = "mean_sd", color = "black",
                  add = "jitter", add.params = list(color = "darkgray"), 
                  ylab = "Supercilium contrast (RGB)", xlab = "Mating strategy") + 
                  scale_x_discrete(labels=c("0"="Monogamous", "1"="Polygynous"))

plot_grid_polygyny <- p_1_polygyny + p_2_polygyny + p_3_polygyny + plot_layout(ncol=3)
print(plot_grid_polygyny)
```

**Figure 3 - Territory Quality**

Relationship between female supercilium a) size, b) brightness, and c) contrast with lores and the index of territory quality in the black-throated blue warbler. The shaded area shows the 95% CI of the best-fit line.

```{r Figure_3, warning=FALSE}
#Size
terr_size <- lm(food_availability ~ s_r_area, data = female_data)
summary(terr_size)

#Brightness
terr_bright <- lm(food_availability ~ s_r_bright, data = female_data)
summary(terr_bright)

#Contrast
terr_cont <- lm(food_availability ~ r_cont, data = female_data)
summary(terr_cont)

# Plot
p_1_territory <- ggscatter(female_data, x = "s_r_area", y = "food_availability", 
          add = "reg.line", conf.int = TRUE, cor.coef = TRUE, cor.method = "pearson",
          xlab = "Supercilium size (mm2)", 
          ylab = "ln caterpillar biomass per territory (mg)")
p_2_territory <- ggscatter(female_data, x = "s_r_bright", y = "food_availability",
          add = "reg.line", conf.int = TRUE, cor.coef = TRUE, cor.method = "pearson",
          xlab = "Supercilium brightness (RGB)", 
          ylab = "ln caterpillar biomass per territory (mg)")
p_3_territory <- ggscatter(female_data, x = "r_cont", y = "food_availability", 
          add = "reg.line", conf.int = TRUE, cor.coef = TRUE, cor.method = "pearson",
          xlab = "Supercilium contrast (RGB)", 
          ylab = "ln caterpillar biomass per territory (mg)")

plot_grid_territory <- p_1_territory + p_2_territory + p_3_territory + plot_layout(ncol=3)
print(plot_grid_territory)
```

**Figure 4 - Male parental effort**

The relationship between female supercilium brightness and male parental effort: a) prey biomass delivered to nestlings, b) nest attentiveness, and c) provisioning rate in the black-throated blue warbler. The shaded area shows the 95% CI of the best-fit line.

```{r Figure_4, warning=FALSE}
#Prey biomass
m_prey_bright <- lm(m_prey ~ s_r_bright, data = female_data)
summary(m_prey_bright)

#Nest attentiveness
m_nest_attentiveness <- lm(m_attent ~ s_r_bright, data = female_data)
summary(m_nest_attentiveness)

#Provisioning rate
m_prov_bright <- lm(m_prov ~ s_r_bright, data = female_data)
summary(m_prov_bright)

#Plot
p_1_prov <- ggscatter(female_data, x = "s_r_bright", y = "m_prey", 
          add = "reg.line", conf.int = TRUE, cor.coef = TRUE, cor.method = "pearson",
          xlab = "Supercilium brightness (RGB)", 
          ylab = "Male prey biomass (mg/nestling/hr)")

p_2_prov <- ggscatter(female_data, x = "s_r_bright", y = "m_attent", 
          add = "reg.line", conf.int = TRUE, cor.coef = TRUE, cor.method = "pearson",
          xlab = "Supercilium brightness (RGB)", 
          ylab = "Male nest attentiveness (sec/nestling/hr)")
p_3_prov <- ggscatter(female_data, x = "s_r_bright", y = "m_prov", 
          add = "reg.line", conf.int = TRUE, cor.coef = TRUE, cor.method = "pearson",
          xlab = "Supercilium brightness (RGB)", 
          ylab = "Male provisioning rate (visits/nestling/hr)")

plot_grid_m_prov <- p_1_prov + p_2_prov + p_3_prov + plot_layout(ncol=3)
print(plot_grid_m_prov)
```

## [Tables]{style="color:royalblue"}

**Table 1 - Female individual quality**

```{r Table_1, warning=FALSE}
#REPRODUCTIVE SUCCESS
#Fecundity
fecund_size <- glm(n_fledge ~ s_r_area, data = female_data, family = poisson)
summary(fecund_size)
fecund_bright <- glm(n_fledge ~ s_r_bright, data = female_data, family = poisson)
summary(fecund_bright)
fecund_contrast <- glm(n_fledge ~ r_cont, data = female_data, family = poisson)
summary(fecund_contrast)

#Attempted a second brood
db_att_size <-glm(db_att ~ s_r_area, data = female_data, family = binomial(link=logit))
summary(db_att_size)
db_att_bright <-glm(db_att ~ s_r_bright, data = female_data, family = binomial(link=logit))
summary(db_att_bright)
db_att_contrast <-glm(db_att ~ r_cont, data = female_data, family = binomial(link=logit))
summary(db_att_contrast)

# Fledged two broods
db_succ_size <-glm(db_succ ~ s_r_area, data = female_data, family = binomial(link=logit))
summary(db_succ_size)
db_succ_bright <-glm(db_succ ~ s_r_bright, data = female_data, family = binomial(link=logit))
summary(db_succ_bright)
db_succ_contrast <-glm(db_succ ~ r_cont, data = female_data, family = binomial(link=logit))
summary(db_succ_contrast)

#Clutch initiation date
cid_size <- lm(cid ~ s_r_area, data = female_data)
summary(cid_size)
cid_brightness <- lm(cid ~ s_r_bright, data = female_data)
summary(cid_brightness)
cid_contrast <- lm(cid ~ r_cont, data = female_data)
summary(cid_contrast)


#FEMALE PARENTAL EFFORT
#Provisioning rate
f_prov_size <- lm(f_prov ~ s_r_area, data = female_data)
summary(f_prov_size)
f_prov_bright <- lm(f_prov ~ s_r_bright, data = female_data)
summary(f_prov_bright)
f_prov_cont <- lm(f_prov ~ r_cont, data = female_data)
summary(f_prov_cont)

#Prey biomass delivered
f_bio_size <- lm(f_prey ~ s_r_area, data = female_data)
summary(f_bio_size)
f_bio_bright <- lm(f_prey ~ s_r_bright, data = female_data)
summary(f_bio_bright)
f_bio_cont <- lm(f_prey ~ r_cont, data = female_data)
summary(f_bio_cont)

#Nest attentiveness
f_attent_size <- lm(f_attent ~ s_r_area, data = female_data)
summary(f_attent_size)
f_attent_bright <- lm(f_attent ~ s_r_bright, data = female_data)
summary(f_attent_bright)
f_attent_cont <- lm(f_attent ~ r_cont, data = female_data)
summary(f_attent_cont)


#MATING STATUS
polygynous_size <- glm(polygynous ~ s_r_area, data = female_data, family = binomial())
summary(polygynous_size)
polygynous_bright <- glm(polygynous ~ s_r_bright, data = female_data, family = binomial())
summary(polygynous_bright)
polygynous_cont <- glm(polygynous ~ r_cont, data = female_data, family = binomial())
summary(polygynous_cont)


#TERRITORY QUALITY
territory_size <- lm(food_availability ~ s_r_area, data = female_data)
summary(territory_size)
territory_bright <- lm(food_availability ~ s_r_bright, data = female_data)
summary(territory_bright)
territory_cont <- lm(food_availability ~ r_cont, data = female_data)
summary(territory_cont)
```

**Table 2 - Male parental effort**

```{r Table_2, warning=FALSE}

# Male parental effort

#Supercilium size - Male provisioning rate
# r = -0.15, p = 0.35
ggscatter(female_data, x = "s_r_area", y = "m_prov", 
          add = "reg.line", conf.int = TRUE, 
          cor.coef = TRUE, cor.method = "pearson",
          xlab = "Right Supercilium Size (mm2)", 
          ylab = "Male Provisioning Rate (visits/nestling/hr)", 
          main = "Supercilium Size and Male Provisioning Rate")

m_prov_size <- lm(m_prov ~ s_r_area, data = female_data)
summary(m_prov_size)

#Supercilium size - Male provisioning rate
# r = -0.026, p = 0.87
ggscatter(female_data, x = "s_r_area", y = "m_prey", 
          add = "reg.line", conf.int = TRUE, 
          cor.coef = TRUE, cor.method = "pearson",
          xlab = "Right Supercilium Size (mm2)", 
          ylab = "Male Prey Biomass (mg/nestling/hr)", 
          main = "Supercilium Size and Male Prey Biomass")

m_bio_size <- lm(m_prey ~ s_r_area, data = female_data)
summary(m_bio_size)

#Supercilium size - Male nest attentiveness
# r = -0.11, p = 0.48
ggscatter(female_data, x = "s_r_area", y = "m_attent", 
          add = "reg.line", conf.int = TRUE, 
          cor.coef = TRUE, cor.method = "pearson",
          xlab = "Right Supercilium Size (mm2)", 
          ylab = "Male Nest Attentiveness (sec/nestling/hr)", 
          main = "Supercilium Size and Male Nest attentiveness")

m_attent_size <- lm(m_attent ~ s_r_area, data = female_data)
summary(m_attent_size)

#Supercilium brightness - Male provisioning rate
# r = 0.42, p = 0.052
p_3_prov <- ggscatter(female_data, x = "s_r_bright", y = "m_prov", 
          add = "reg.line", conf.int = TRUE, 
          cor.coef = TRUE, cor.method = "pearson",
          xlab = "Supercilium brightness (RGB)", 
          ylab = "Male provisioning rate (visits/nestling/hr)")

m_prov_bright <- lm(m_prov ~ s_r_bright, data = female_data)
summary(m_prov_bright)

#Supercilium brightness - Male prey biomass
# r = 0.47, p = 0.029
p_1_prov <- ggscatter(female_data, x = "s_r_bright", y = "m_prey", 
          add = "reg.line", conf.int = TRUE, 
          cor.coef = TRUE, cor.method = "pearson",
          xlab = "Supercilium brightness (RGB)", 
          ylab = "Male prey biomass (mg/nestling/hr)")

m_prey_bright <- lm(m_prey ~ s_r_bright, data = female_data)
summary(m_prey_bright)

#Supercilium brightness - Male nest attentiveness
# r = 0.44, p = 0.041

p_2_prov <- ggscatter(female_data, x = "s_r_bright", y = "m_attent", 
          add = "reg.line", conf.int = TRUE, 
          cor.coef = TRUE, cor.method = "pearson",
          xlab = "Supercilium brightness (RGB)", 
          ylab = "Male nest attentiveness (sec/nestling/hr)")

m_prey_attent <- lm(m_attent ~ s_r_bright, data = female_data)
summary(m_prey_attent)

plot_grid <- p_1_prov + p_2_prov + p_3_prov + plot_layout(ncol=3)
print(plot_grid)

#Supercilium contrast - Male provisioning rate
# r = -0.27, p = 0.23
m_bio_contrast <- lm(m_prey ~ r_cont, data = female_data)
summary(m_bio_contrast)

ggscatter(female_data, x = "r_cont", y = "m_prov", 
          add = "reg.line", conf.int = TRUE, 
          cor.coef = TRUE, cor.method = "pearson",
          xlab = "Right Supercilium Contrast (RGB)", 
          ylab = "Male Provisioning Rate (visits/nestling/hr)", 
          main = "Supercilium Contrast and Male Provisioning Rate")

#Supercilium contrast - Male prey biomass
# r = -0.086, p = 0.70
m_bio_contrast <- lm(m_prey ~ r_cont, data = female_data)
summary(m_bio_contrast)

ggscatter(female_data, x = "r_cont", y = "m_prey", 
          add = "reg.line", conf.int = TRUE, 
          cor.coef = TRUE, cor.method = "pearson",
          xlab = "Right Supercilium Contrast (RGB)", 
          ylab = "Male Prey Biomass (mg/nestling/hr)", 
          main = "Supercilium Brightness and Male Prey Biomass")

#Supercilium contrast - Male nest attentiveness
m_atten_contrast <- lm(m_attent ~ r_cont, data = female_data)
summary(m_atten_contrast)

# r = -0.16, p = 0.47
ggscatter(female_data, x = "r_cont", y = "m_attent", 
          add = "reg.line", conf.int = TRUE, 
          cor.coef = TRUE, cor.method = "pearson",
          xlab = "Right Supercilium Contrast (RGB)", 
          ylab = "Male Nest Attentiveness (sec/nestling/hr)", 
          main = "Supercilium Brightness and Male Nest Attentiveness")


```

## [Additional results]{style="color:royalblue"}

**Plumage Variation**

```{r Plumage_variation, warning=FALSE}
#SUPERCILIUM SYMMETRY
#Size
ggscatter(female_data, x = "s_r_area", y = "s_l_area", 
          add = "reg.line", conf.int = TRUE, cor.coef = TRUE, cor.method = "pearson",
          xlab = "Right Supercilium Size (mm2)", 
          ylab = "Left Supercilium Size (mm2)", main = "Supercilium Size Symmetry")
#Brightness
ggscatter(female_data, x = "s_r_bright", y = "s_l_bright", 
          add = "reg.line", conf.int = TRUE, cor.coef = TRUE, cor.method = "pearson",
          xlab = "Right Supercilium Brightness (RGB)", 
          ylab = "Left Supercilium Brightness (RGB)", 
          main = "Supercilium brightness symmetry")
#Contrast
ggscatter(female_data, x = "r_cont", y = "l_cont", 
          add = "reg.line", conf.int = TRUE, cor.coef = TRUE, cor.method = "pearson",
          xlab = "Right contrast (RGB)", ylab = "Left contrast (RGB)", 
          main = "Contrast symmetry")


#CORRELATIONS BETWEEN SUPERCILIUM MEASURES 
#Size and contrast
p_3_plumage <- ggscatter(female_data, x = "s_r_area", y = "r_cont", 
          add = "reg.line", conf.int = TRUE, cor.coef = TRUE, cor.method = "pearson",
          xlab = "Right Supercilium Brightness (RGB)", 
          ylab = "Supercilium Contrast (RGB)", main = "Supercilium Size and Contrast")
#Size and brightness
ggscatter(female_data, x = "s_r_bright", y = "s_r_area", 
          add = "reg.line", conf.int = TRUE, cor.coef = TRUE, cor.method = "pearson",
          xlab = "Right Supercilium Brightness (RGB)", 
          ylab = "Right Supercilium Size (mm2)", main = "Supercilium Size and Brightness")
#Brightness and contrast
ggscatter(female_data, x = "s_r_bright", y = "r_cont", 
          add = "reg.line", conf.int = TRUE, cor.coef = TRUE, cor.method = "pearson",
          xlab = "Right Supercilium Brightness (RGB)", 
          ylab = "Facial Contrast (RGB)", main = "Supercilium brightness and contrast")


#CORRELATIONS BETWEEN UNDER-EYE MARK AND SUPERCILUM
#Size
p_1_plumage <- ggscatter(female_data, x = "s_r_area", y = "u_r_area", 
          add = "reg.line", conf.int = TRUE, 
          cor.coef = TRUE, cor.method = "pearson",
          xlab = "Right Supercilium Size (mm2)", 
          ylab = "Right Under-eye Size (mm2)", 
          main = "Right Supercilium and Under-eye Size")
#Brightness
p_2_plumage <- ggscatter(female_data, x = "s_r_bright", y = "u_r_bright", 
          add = "reg.line", conf.int = TRUE, cor.coef = TRUE, cor.method = "pearson",
          xlab = "Right Supercilium Brightness (RGB)", 
          ylab = "Right Under-eye Brightness (RGB)",
          main = "Supercilium and Under-eye Brightness")
```

## [Supplementary Results]{style="color:royalblue"}

**Figure S2 - Distributions of supercilium size, brightness, and contrast**

Histograms of three measures of female supercilium conspicuousness, including a) size, b) brightness, and c) contrast with lores, showing the ranges and distributions of these measures in the black-throated blue warbler.

```{r Figure_S2, warning=FALSE}
#Size
hist(female_data$s_r_area, breaks = 15, main = "Histogram of supercilium size 2021-2023", 
     xlab = "Supercilium size (mm2)")
range(female_data$s_r_area)
mean(female_data$s_r_area) 
sd(female_data$s_r_area)
length(female_data$s_r_area)

#Brightness
hist(female_data$s_r_bright, breaks = 15,
     main = "Histogram of supercilium brightness 2021, 2023", 
     xlab = "Supercilium brightness (RGB)")
range(female_data$s_r_bright, na.rm=TRUE)
mean(female_data$s_r_bright, na.rm=TRUE) 
sd(female_data$s_r_bright, na.rm=TRUE)
length(female_data$s_r_bright[!is.na(female_data$s_r_bright)])

#Contrast
hist(female_data$r_cont, breaks = 8, main = "Histogram of supercilium contrast 2021, 2023",
     xlab = "Supercilium contrast (RGB)")
range(female_data$r_cont, na.rm=TRUE)
mean(female_data$r_cont, na.rm=TRUE) 
sd(female_data$r_cont, na.rm=TRUE)
length(female_data$r_cont[!is.na(female_data$r_cont)])
```

**Table S1 - Conspicuousness and other individual characteristics**

Linear model, t-test, and ANOVA results examining associations between female supercilium conspicuousness measures and body size, age class, year, and elevation zone in the black-throated blue warbler.

```{r Table_S1, warning=FALSE}
#BODY SIZE
#Tarsus length
f_size_tarsus <- lm(tarsus ~ s_r_area, data = female_data)
summary(f_size_tarsus)
f_bright_tarsus <- lm(tarsus ~ s_r_bright, data = female_data)
summary(f_bright_tarsus)
f_cont_tarsus <- lm(tarsus ~ r_cont, data = female_data)
summary(f_cont_tarsus)
#Culmen length
f_size_culmen <- lm(nares ~ s_r_area, data = female_data)
summary(f_size_culmen)
f_bright_culmen <- lm(nares ~ s_r_bright, data = female_data)
summary(f_bright_culmen)
f_cont_culmen <- lm(nares ~ r_cont, data = female_data)
summary(f_cont_culmen)
#Mass
f_size_mass <- lm(mass ~ s_r_area, data = female_data)
summary(f_size_mass)
f_bright_mass <- lm(mass ~ s_r_bright, data = female_data)
summary(f_bright_mass)
f_cont_mass <- lm(mass ~ r_cont, data = female_data)
summary(f_cont_mass)
# Age
t.test(female_data$s_r_area ~ female_data$age)
t.test(female_data$s_r_bright ~ female_data$age)
t.test(female_data$r_cont ~ female_data$age)
# Year
size.year.aov <- aov(s_r_area ~ factor(year), data = female_data)
summary(size.year.aov)
bright.year.aov <- aov(s_r_bright ~ factor(year), data = female_data)
summary(bright.year.aov)
cont.year.aov <- aov(r_cont ~ factor(year), data = female_data)
summary(cont.year.aov)
# Elevation
size.elev.aov <- aov(s_r_area ~ factor(elevation), data = female_data)
summary(size.elev.aov)
bright.elev.aov <- aov(s_r_bright ~ factor(elevation), data = female_data)
summary(bright.elev.aov)
cont.elev.aov <- aov(r_cont ~ factor(elevation), data = female_data)
summary(cont.elev.aov)
```

**Table S2 - Territory quality and parental behavior**

```{r Territory quality and parental behavior, warning=FALSE}
#Males
male_prey_territory <- lm(m_prey ~ food_availability, data = female_data)
summary(male_prey_territory)
male_nest_territory <- lm(m_attent ~ food_availability, data = female_data)
summary(male_nest_territory)
male_prov_territory <- lm(m_prov ~ food_availability, data = female_data)
summary(male_prov_territory)
#Females 
female_prey_territory <- lm(f_prey ~ food_availability, data = female_data)
summary(female_prey_territory)
female_nest_territory <- lm(f_attent ~ food_availability, data = female_data)
summary(female_nest_territory)
female_prov_territory <- lm(f_prov ~ food_availability, data = female_data)
summary(female_prov_territory)
#Within-pair difference
delta_prey_bright <- lm(delta_prey ~ food_availability, data = female_data)
summary(delta_prey_bright)
delta_nest_attentiveness <- lm(delta_attent ~ food_availability, data = female_data)
summary(delta_nest_attentiveness)
delta_prov <- lm(delta_prov ~ food_availability, data = female_data)
summary(delta_prov)
```
